GRB Afterglows In The Multi-Messenger Era OR Electromagnetic Afterglows Of Structured Jets OR Structured Jets At All Angles

### 2019-05-08 structuredJets.tex
Fixed figure sizes, added light curve grid figure

\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

@@

\begin{figure}
	\plotone{figs/jetStructureComparison.pdf}
	\caption{Lateral profiles of isotropic equivalent energy $\Eiso$ as a function of angle from the jet axis $\theta$, individually rescaled to group similar profile shapes.  The thick grey lines show fiducial profiles with simple analytic expressions (Equations \eqref{eq:gauss} and \eqref{eq:pl}) while the thin colored lines show results from numerical simulations and analytic models chosen from the literature.  The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), and purple the numerical simulation from \cite{Margutti:2018aa} (M18).  The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a smoothed power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 4^\circ$, $\thW=20^\circ$, and $b=4.5$.  The Gaussian and power law profiles can emulate the basic properties of the energy profiles found in the literature. \label{fig:jetStruct}}
\end{figure}

@@

%These errors quoted are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.  That is, they are the errors relative to solving these equations perfectly.  The equations themselves are, however, an approximation themselves to the full physics of an afterglow light curve.  Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.  
%
\begin{figure*}
	\plotone{figs/boxfit_comp.pdf}
	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines). Bottom Panel: Fractional difference between \afterglowpy{} and \boxfit{} light curves.  Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), x-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and x-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).  Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$. \label{fig:boxfitComp}}
\end{figure*}

@@

@@

We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$). In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.  There is little to distinguish between different structure $E(\theta)$, and the light curve is well-approximated by a broken power law with characteristic break times.  The \emph{misaligned} light curve also may present as a broken power law, but with closure relations explicitly dependent on viewing angle and jet angular structure.

@@

The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{sec:derive1}) by:
\begin{align}
	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} .\label{eq:tbpm}
\end{align}
\begin{figure}
	\plotone{figs/breaks_alignedOA_all.pdf}
	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$. The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thC/2)^{8/3}$. These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$. \label{fig:tbOA}}
\end{figure}

@@

\begin{figure}
	\plotone{figs/lc_on.pdf}
	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets. When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.  The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.  These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc. \label{fig:onaxis}}
\end{figure}

@@

\begin{figure}
	\plotone{figs/jetDecomp.pdf}
	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.  The off-axis, structured, and post-jet break phases are all clearly visible.  The structured phase is the result of the brightest point of the blast-wave tracking from the wings $(\theta =\thW$) to the jet core ($\theta=\thC$). \label{fig:decomp}}
\end{figure}
Figure \ref{fig:decomp} shows the light curve of a Gaussian structured jet along with the emissions from different latitudes.  The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$. The angular size of the visible patch grows approximately as $\gamma^{-1.0}$. (NEED PLOT?)

@@

\begin{figure}
	\plotone{figs/lc_off1.pdf}
	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.  The top-hat jet (with opening angle $\thC$) begins in the off-axis phase.  The Gaussian and power law jets begin in the structured phase as $\thobs < \thW$.  All three models enter similar post-jet break phases. \label{fig:offaxis1}}
\end{figure}
\begin{figure}
	\plotone{figs/lc_off2.pdf}
	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$. All three models exhibit off-axis, structured, and post-jet break phases of evolution.  At larger opening angles the difference between structured models is more evident.  \label{fig:offaxis2}}
\end{figure}

@@

\begin{figure}
	\plotone{figs/slopesJet.png}
	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).  The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.  The temporal power law slope of a structured jet afterglow increases with $g$ in all spectral regimes. \label{fig:slopesG}}
\end{figure}

@@

\begin{figure}
	\plotone{figs/slopesCocoon.png}
	\caption{The temporal power law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.  Otherwise as Figure \ref{fig:slopesG}.  The temporal power law slope of a structured jet afterglow increases with $k$ in all spectral regimes. \label{fig:slopesK}}
\end{figure}

@@

\begin{figure*}
	\plotone{figs/cornerGaussian.png}
	\caption{Views of the posterior parameter distribution for a Gaussian jet fit to the \gwbns{} afterglow.  The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters. \label{fig:cornerGaussian}}
\end{figure*}

\begin{figure*}
	\plotone{figs/cornerPowerlaw.png}
	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.  The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters. \label{fig:cornerPowerlaw}}
\end{figure*}

@@

\begin{figure}
	\plotone{figs/g_plot.pdf}
	\caption{Structure parameter $g$ as a function of $\thobs/\thC$ for different structured jet models: Gaussian (blue), $b=2$ power law (orange), $b=4$ power law (green), and $b=6$ power law (red).  The inferred value $g = 8.2\pm0.5$ for \gwbns{} is shown in as the grey band. \label{fig:gPop}}
\end{figure}

>>>>

\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
%\hypersetup{
%    colorlinks=true,
%    linkcolor=blue,
%    filecolor=magenta,      
%    urlcolor=cyan,
%}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/jetStructureComparison.pdf}
	\caption{Lateral profiles of isotropic equivalent energy $\Eiso$ as a function of angle from the jet axis $\theta$, individually rescaled to group similar profile shapes.  The thick grey lines show fiducial profiles with simple analytic expressions (Equations \eqref{eq:gauss} and \eqref{eq:pl}) while the thin colored lines show results from numerical simulations and analytic models chosen from the literature.  The blue line is the B1 numerical simulation of \cite{Aloy:2005aa}, orange the HE16N numerical simulation of \cite{Mizuta:2009aa}, green an analytic ``boosted fireball'' model with $\gamma_{\rm{B}}=10$ and $\eta_0=3$ from \cite{Duffell:2013aa}, red the numerical simulation from \cite{Lazzati:2017aa} (L17), and purple the numerical simulation from \cite{Margutti:2018aa} (M18).  The thick solid grey line is a Gaussian profile (Equation \eqref{eq:gauss}) with $E_0 = 3\times 10^{52}$ erg, $\thC = 6^\circ$, and $\thW=12^\circ$ and the thick dashed grey line is a smoothed power law profile (Equation \eqref{eq:pl}) with $E_0 = 10^{52}$ erg, $\thC = 4^\circ$, $\thW=20^\circ$, and $b=4.5$.  The Gaussian and power law profiles can emulate the basic properties of the energy profiles found in the literature. \label{fig:jetStruct}}
\end{figure}

@@

%These errors quoted are numerical errors associated with the schemes used to solve Equations \ref{eq:Rdot}, \ref{eq:E}, and \ref{eq:thetadot} and perform the integral in Equation \ref{eq:flux2}.  That is, they are the errors relative to solving these equations perfectly.  The equations themselves are, however, an approximation themselves to the full physics of an afterglow light curve.  Comparison and calibration against analytic calculations and hydrodynamic simulations is necessary to ensure physically realistic results.  
%
\begin{figure*}
	\includegraphics[width=\textwidth]{figs/boxfit_comp.pdf}
	\caption{Top Panel: Comparison between top hat jet light curves from \afterglowpy{} (solid lines) and \boxfit{} (dashed lines). Bottom Panel: Fractional difference between \afterglowpy{} and \boxfit{} light curves.  Four representative light curves are shown: radio on-axis ($\thobs=0$, $\nu=10^9$Hz, blue), radio off-axis ($\thobs=0.16$rad, $\nu=10^9$Hz, orange), x-ray on-axis ($\thobs=0$, $\nu=10^{18}$Hz, green), and x-ray off-axis ($\thobs=0.16$rad, $\nu=10^{18}$Hz, red).  Remaining parameters are shared: $\thC=0.1$rad, $\Eiso=10^{52}$erg, $n_0 = 10^{-3}$cm$^{-3}$, $p=2.2$, $\epse=10^{-1}$, $\epsB=10^{-2}$, $\dL=3.09 \times 10^{26}$cm, $z=0.028$. \label{fig:boxfitComp}}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%
%
% Afterglows Section
%
%%%%%%%%%%%%%%%%%%%%

@@

We find the light curves of structured jets show two modes of behaviour, depending on whether the observer is \emph{aligned} ($\thobs < \thC$) or \emph{misaligned} ($\thobs > \thC$) TODO: CITE PREVIOUS STRUCTURED JET WORK
 In the \emph{aligned} case, the light curves follow the standard on-axis top hat behaviour modified slightly for non-zero viewing angle.  There is little to distinguish between different structure $E(\theta)$, and the light curve is well-approximated by a broken power law with characteristic break times \citep{Granot:2002aa}.  The \emph{misaligned} light curve also may present as a broken power law, but with closure relations explicitly dependent on viewing angle and jet angular structure.

@@

The transition between pre-jet break and post-jet break begins at $\tbm$ and completes at $\tbp$, given in the single shell approximation (see Appendix \ref{sec:derive1}) by:
\begin{align}
	\tbpm &= \left(\frac{9}{16\pi} \frac{E_0}{n_0 \Mp c^5}\right)^{1/3} \left( 2 \sin \left(\frac{\thC\pm\thobs}{2}\right)\right)^{8/3} .\label{eq:tbpm}
\end{align}
\begin{figure}
	\includegraphics[width=\columnwidth]{figs/breaks_alignedOA_all.pdf}
	\caption{Jet break time for on-axis ($\thobs=0$) observers for top-hat (blue circles), Gaussian (orange squares), and power law (green triangles) jets as a function of $\thC$. The dashed grey line is the analytic approximation $\tbpm = t_N (2\sin \thC/2)^{8/3}$. These particular light curves use $\thW = 5 \thC$, $E_0 = 10^{52}$erg, $n_0=10^{-3}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, and $\epsB = 10^{-4}$. \label{fig:tbOA}}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/lc_on.pdf}
	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets. When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.  The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.  These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc. \label{fig:onaxis}}
\end{figure}

\begin{figure*}
	\includegraphics[width=\textwidth]{figs/lc_thV_model_multi.pdf}
	\caption{Aligned ($\thobs = \thC/2$) afterglow light curves for top-hat (blue), Gaussian (orange), and power law (green) jets. When viewed on-axis, jets containing angular structure are very difficult to distinguish from top-hats.  The transition phase marking the onset of the jet break begins at $\tbm\sim3$ days with a shallow break and ends sharply at $\tbp \sim 100$ days.  These particular light curves use $\thC = 0.1$ rad, $\thW = 0.4$ rad, $E_0 = 10^{52}$erg, $n_0=10^{-2}$cm$^{-3}$, $p=2.2$, $\epse = 10^{-1}$, $\epsB = 10^{-3}$, and $d_L=40$Mpc. \label{fig:onaxis}}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/jetDecomp.pdf}
	\caption{A Gaussian structured jet, decomposed into emission from different latitudes $\theta$.  The off-axis, structured, and post-jet break phases are all clearly visible.  The structured phase is the result of the brightest point of the blast-wave tracking from the wings $(\theta =\thW$) to the jet core ($\theta=\thC$). \label{fig:decomp}}
\end{figure}
Figure \ref{fig:decomp} shows the light curve of a Gaussian structured jet along with the emissions from different latitudes.  The part of the blast wave dominating the emission tracks from the high latitude wings $\theta \approx \thW$ to the core $\theta \approx 0$. The angular size of the visible patch grows approximately as $\gamma^{-1.0}$. (NEED PLOT?)

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/lc_off1.pdf}
	\caption{As Figure \ref{fig:onaxis} but $\thobs = 2\thC$.  The top-hat jet (with opening angle $\thC$) begins in the off-axis phase.  The Gaussian and power law jets begin in the structured phase as $\thobs < \thW$.  All three models enter similar post-jet break phases. \label{fig:offaxis1}}
\end{figure}
\begin{figure}
	\includegraphics[width=\columnwidth]{figs/lc_off2.pdf}
	\caption{As Figure \ref{fig:onaxis} but $\thobs = 6\thC$. All three models exhibit off-axis, structured, and post-jet break phases of evolution.  At larger opening angles the difference between structured models is more evident.  \label{fig:offaxis2}}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/slopesJet.png}
	\caption{Temporal slopes for the off-axis structured jet as a function of the structure parameter $g$ for the synchrotron spectral regimes D (blue, narrow), E (orange, narrow),  F (green, narrow), G (red, wide), and H (purple, wide).  The width of the G and H bands shows the dependency on $p$, the upper curves for $p=2$ and the lower for $p=3$.  The temporal power law slope of a structured jet afterglow increases with $g$ in all spectral regimes. \label{fig:slopesG}}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/slopesCocoon.png}
	\caption{The temporal power law slope of the spherical refreshed-shock afterglow light curve as a function of $k$.  Otherwise as Figure \ref{fig:slopesG}.  The temporal power law slope of a structured jet afterglow increases with $k$ in all spectral regimes. \label{fig:slopesK}}
\end{figure}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figs/cornerGaussian.png}
	\caption{Views of the posterior parameter distribution for a Gaussian jet fit to the \gwbns{} afterglow.  The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters. \label{fig:cornerGaussian}}
\end{figure*}

\begin{figure*}
	\includegraphics[width=\textwidth]{figs/cornerPowerlaw.png}
	\caption{Views of the posterior parameter distribution for a power law jet fit to the \gwbns{} afterglow.  The diagonal contains one-dimensional marginalized posteriors for each fit parameter, while the off-diagonal plots contain two-dimensional maps of the posterior marginalized over all but the two corresponding parameters. \label{fig:cornerPowerlaw}}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figs/g_plot.pdf}
	\caption{Structure parameter $g$ as a function of $\thobs/\thC$ for different structured jet models: Gaussian (blue), $b=2$ power law (orange), $b=4$ power law (green), and $b=6$ power law (red).  The inferred value $g = 8.2\pm0.5$ for \gwbns{} is shown in as the grey band. \label{fig:gPop}}
\end{figure}
